\documentclass{article}
\usepackage{../csci-246-fall2018/hw/template/fasy-hw}

\author{Nathan Stouffer}
\problem{1-1}
\collab{none}

\begin{document}

My photo in D2L has been updated to be a clearly identifiable photo.

\problem{1-2}
\collab{none}
\clearpage
\header
This assignment uses the homework template.

\problem{1-3}
\collab{none}
\clearpage
\header
\begin{itemize}
	\item Algorithms: Coded search and sort algorithms in Java and Python
	\item Data Structures: Coded linked lists, trees, stacks, and queues in Java
	\item Graphs: Only the knowledge that they consist of nodes and lines
	\item Binomial Coefficients: No experience
	\item Proof by Counter-example: Proving simple statements
	\item Proof by Example: Proving simple statements
	\item Proof by Induction: No experience
	\item Recursion in Code: Using recursion in CSCI 127 and CSCI 132
	\item Recurrence Relations: No experience
	\item The Four Color Theorem: No experience
\end{itemize}

\problem{1-4}
\collab{none}
\clearpage
\header
I have reviewed all properties of real numbers in Appendix A.

\problem{1-5}
\collab{Kevin Browder}
\clearpage
\header
Prove there are distinct integers \emph{m} and \emph{n} such that $\dfrac{1}{m}+\dfrac{1}{n} \in \mathbb{Z}$
\begin{center}
	\underline{Proof by Example}
\end{center}
If m = 1 and n = -1, then the equation reads $\dfrac{1}{1}+\dfrac{1}{-1}=0$ where m, n, and the solution are all integers

\problem{1-6}
\collab{Kevin Browder}
\clearpage
\header
Prove the product of any even integer and any integer is even
\\\\
Statement: An integer is even if it is divisible by two.
\\
Any given even integer, A, can be written as $2*B$ where $B=\dfrac{A}{2}$. Therefore, the product of A and any integer, C, will be even because it is equivalent to $2*B*C$, which is divisible by 2

\problem{1-7}
\collab{Kevin Browder}
\clearpage
\header
Sets A and D are equal

\problem{1-8}
\collab{Kevin Browder}
\clearpage
\header
The relation \emph{T}, defined as $y^{2}-x^{2}=1$, is not a function because it does not satisfy the following property:
\begin{center}
	For all elements x in A and y and z in B, if  \(x,y\) $\in$ \emph{F} and \(x,z\) $\in$ \emph{F}, then y = z
	
	\underline{Proof by Counter-example}
\end{center}
If x = 0, then \emph{T} will be $y^{2} = 1$. At this point, y could be defined as 1 or -1 to satisfy the relation, which proves that \emph{T} is not a function.

\problem{1-9}
\collab{none}
\clearpage
\header
Georg Cantor was a German mathematician in the mid 1800s that focused much of his work on the nature of different types of infinities. Regarding computer science, Cantor was one of the pioneers of set theory, which we will deal with a lot on this class. According to the Encyclopedia Britannica, Cantor developed sets of numbers from the integers to irrationals \cite{Britinnica}. We use sets in computer science to organize information and draw relations between different data.

\newpage
\begin{thebibliography}{9}
	\bibitem{Britinnica} The Editors of Encyclopedia Britannica "Georg Cantor." Encyclopedia Britannica. Encyclopedia Britannica Inc., 2018. Britannica. Web. Sep 4, 2018.
\end{thebibliography}

\end{document}

